### 2013-12-02 inst/doc/manuscript.Rmd
use slots instead of representation. closes #47

@@

### Reading NeXML phylogenies

```{r}
phy = read.nexml("trees.xml", as="phylo")
plot(phy)
```

>>>>

A nexml file can be thought of as having three components: (1) phylogeny data (2) character-trait data, and (3) metadata. `RNeXML` seeks to provide a seemless way to convert these to and from their corresponding R object representations, such as `ape::phylo` phylogenies, character matrices (`data.frames`) and metadata lists (or for advanced users, `XMLInternalDocument` and `rrdf` triplestores).  The RNeXML package functions (the package Application Programming Interface, API)

@@

<!-- Do we describe installation of the package?  `install.packages("RNeXML")`?-->

### Reading NeXML

```{r echo=FALSE}
library(RNeXML)
```

We begin by reading in an example NeXML file.

```{r}
f <- system.file("examples", "trees.xml", package="RNeXML")
nex <- read.nexml("trees.xml")
```

The resulting `nex` object is an R
